\documentclass{article}
\usepackage{fullpage}

\renewcommand{\familydefault}{\sfdefault}
\usepackage[scaled=1]{helvet}
\usepackage[helvet]{sfmath}
\everymath={\sf}

\usepackage{parskip}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Klamath Bible}
\author{John "notgull" Nunley}
%\company{Eel Removal}
\setcounter{tocdepth}{2}
\begin{document}
\maketitle
\tableofcontents

\setlength{\parindent}{4em}
\setlength{\parskip}{1em}

\section{Introduction} 
This is a design document for my idea of a "Detective Klamath" animated series. This document contains the ideas of the history, general structure of episode and series, and overarching themes for a cartoon with themes regarding the hardships involved in the creation process, as well as urban warfare and irony.

If you have received this document, it is likely you're working directly on Detective Klamath with me, notgull. If you are, please do not share this document, as it could spoil the series or affect the audience's perception of it.

\subsection{General Overview}

Detective Klamath is a comedy-drama, starring the titular gooian Detective Klamath Tellth attempting to single-handedly bring down a conspiracy involving Reno nuclear energy magnate Roth Darkmond taking control of Reno's economy. Despite having his private-eye license revoked after a previous attempt to confront Darkmond and being overall ill-prepared to fight the conspiracy, he persists on regardless. He is assisted by his best friend and roommate Dr. Jack Chester, a lazy inventor and scientist. He is both allied with and against Officer Shirley Signage, a police officer involved in Klamath's antics in the past who holds a pessimistic view on life in general. Early on in the series, Darkmond hires the incompetent hitman Thomas Clearway to prevent Klamath from pursuing the truth regarding his conspiracy. Occasionally, they are joined by Klamath and Jack's landlord, Metalman, a boomer Vietnam veteran. These characters make up the series' main cast.

Detective Klamath is set in a world where, after a long series of alien invasions, animal uprisings, and AI takeovers, humanity is now living alongside a litany of various other races in relative harmony. In the town of Reno, Nevada, humans are still dominant, although various other races still live alongside them. This harmony is kept by the shadowy Upper Council, a group consisting of important figures from these various races that keep the general populace in check.

Each episode should consist of Klamath following a lead, often with the help of Chester or Shirley. Thomas attempts to use the lead to his advantage to kill Klamath. However, the characters inevitably encounters some kind of faux-pa that spirals into the main conflict of the episode. Klamath attempts to use something demonstrated earlier in the episode to resolve the conflict, but this only makes it worse. However, something subtly hinted at even earlier in the episode causes the end resolution of the central conflict. In the course of this conflict, Klamath loses any evidence of the conspiracy and is forced to start over.

In the first season, Klamath quits his reporting job and attempts to find evidence of the Darkmond conspiracy in order to prevent it from taking over Reno. Halfway through the season, Klamath's older brother Donald comes and tries to convince Klamath to stop following the, in his eyes, false conspiracy and return to stable employment; however, he notices evidence of the conspiracy and decides to follow it instead. Before Klamath can accumulate even a single piece of evidence, Donald finds evidence of antitrust violations and attempts to bring it to the eyes of the city's mayor. However, the mayor is, in fact, controlled by Darkmond, and Darkmond assassinates Donald during the meeting. Klamath uses his brother's last words as well as the help of a local antitrust agent to finally expose Darkmond. However, in a final shootout with Darkmond, Klamath fatally injures Darkmond at the last second before he can get away. This incident gives Klamath credibility and rises him to mild fame and fortune.

In the second season, Klamath begins to take on odd detective work while he mourns for his brother and keeps a sneaking suspicion that Darkmond wasn't at the top of the food chain. As he resolves these odd jobs, he finds shards of evidence of an "Upper Council" that may have controlled Darkmond from behind the scenes; in fact, the "Upper Council" seems to have hired Thomas to kill Klamath. However, he has an even harder time finding evidence than he did for the Darkmond conspiracy. After Shirley is killed in a shootout that Klamath suspects to be tied to the Upper Council, his suspicions multiply, and his work eventually brings him to an abandoned cabin in the middle of the desert. Here he meets messengers of the Upper Council, who tell him there is a bomb underneath his house that it set to detonate the entire city. He goes back to Reno and finds the bomb defended by Jack, who has been hired by the Upper Council. A fight with Jack leaves Klamath fatally wounded, and he stops the bomb's detonation by shooting himself and then covering the bomb's innards with the goo he is made out of. It should be unclear whether or not the events of the series finale are entirely Klamath's imagination or not.

\section{History}

This section details the history of the world and how it should show through in the series proper.

\subsection{Pre-Invasion}

The timeline of Klamath diverges from our own in 1800. After the French Revolution and American Revolution, the aristocrats of Europe begin to fear that democracies may one day overtake monarchies, essentially dissolving their power. To combat this, they pool their resources and create an elite team of assassins in order to dissolve democracies. These assassins kill Napoleon Bonaparte and cause the end of his empire long before he can stand as a threat.

The revolutions of 1848 lead to these assassins being used more often, even if their assassinations often failed at the intended effect of stopping the reformations. This causes the group to grow in power, until they establish the Upper Council, essentially superseding the monarchies they were originally founded to protect. The Upper Council, in addition to covertly assassinating rulers that stepped out of their line, established institutions of science in order to gain a leg up on the working population.

By the 1900's, the Upper Council's sciences were leagues ahead of contemporary science. Their astronomy division had conclusively identified several alien civilization and even begun to communicate with them. Meanwhile, its biology division had created a number of drugs that could modify the human body to incredible degrees. One of these drugs was Sensodryme, which could exponentially increase the intelligence of a human subject. These drugs were used to microdose rulers to either keep them in power or depose them. Meanwhile, its computing division had invented computers, and were able to use them to simulate world affairs.

With the commencement of World Wars, the Upper Council used its influence to determine which side won the war. Realizing that it could now control a democracy more than a monarchy, it established front companies in the west in order to supply it with a steady drip of weapon advancements. With their help, the western democracies easily win both wars. These front companies remained and supported the Upper Council with a steady supply of profits.

In the series, the Upper Council would likely be behind the events of Season 2, after Klamath successfully defeats Darkmond and attracts their attention. Make sure to sew doubt whether or not the Upper Council is even real or just a figment of Klamath's imagination, trying to come up with a bigger fish of a conspiracy to solve.

\subsection{The First Invasions}

In the early 1950's, the Upper Council began to realize that the relative peace after World War 2 was causing it to lose its grip on the world and, potentially, could lead to one of its puppets rebelling against it. After some early lab trials in a laboratory in Carson City, they decided to enact the Couscous Protocol: to create another intelligent species in order to divide humanity. One of the pharmaceutical front companies, Jasper, underwent an industrial accident and began leaking Sensodryme into the swamps of Florida. Predictably, this caused the crocodiles of Florida to mutate into higher, more intelligent beings. Before the leak was discovered, the new crocodile people were supplied with weapons and technology by the Upper Council, who, in exchange, put their representatives in the Council's seats.

The crocodile people staged a rebellion against humanity, carving out a territory in lower Florida for their civilization. Meanwhile, the Upper Council began to enact the Coucous Protocol for other populations of animals, such as bear people in the Soviet Union, giraffe people in Africa, and penguin people in Antartica, began staging their own rebellions. Humanity at large was shocked, and generally united in war against these new kingdoms.

Meanwhile, the Upper Council notified the aliens in regards to the current war. Some decided to intervene on the side of the humanity or one of the new animal factions, or opportunistically took advantage of the chaos in an attempt to take Earth for themselves.

\subsection{Initial Animal Scrimishes}

At the beginning of the war, the human forces, still in disparate countries, had the advantage. The United States managed to push the alligator forces deep into Florida, while the Soviet Union proceeded to engage in inhumanitarian efforts against the bears.

However, the war began to shift once the alligators began carrying Sensodryme to other swamp areas in the Americas, even extended down as far as Brazil. They became ingrained into the swamps by using a form of guerilla warfare that made any intrusion into these swamps nearly impossible. America started using napalm on the swamps, but this was quickly countered by a long-range missile developed the the alligators that took out planes from outside of their range. Although enthusiasm for the war, fostered by American science fiction propoganda for the public, was initially overflowing, the war effort became exhausted as the alligators turned the war into one of attrition.

Meanwhile, the Metalmen of Dosi 13 had rushed to Earth and allied with the bears in order to carve out a territory in Siberia. The Metalmen's technology, combined with that of the Upper Council, allowed the bears to establish an unprecedented industrial complex in their territory. Although they were unable to out-industrialize the Soviet Union, their numbers and usage of guerilla warfare allowed them to push back the combined Sino-Soviet army. In addition, the penguin people of Antartica had seized warships near the Antartic and established themselves as a terrifying effective navy. Seeing their cause as united, they allied with both the bear and the alligators in order to prevent their respective human forces from gaining an advantage at sea.

In addition, the giraffe people quickly attained the technology to effectively control the heartland of Africa. They began to cross the Mediterranean sea, preventing the European countries from sending aid to the United States, further exhausting their efforts. However, a misapplication of Sensodryme gave the cheetas sapience as well, and they entered into war with the giraffes.

By the end of 1952, the humans appeared to be ahead in the war. The American countries had largely isolated the alligator threat to the southern United States and upper Mexico, even without navy support, and the combined bear/Metalmen forces underwent diplomatic conflicts and essentially infighting. The giraffe/cheeta infighting had also reduced their effectiveness.

However, the entire landscape of the conflict was changed when the Gooians and the Grayheads began their invasion.

\subsection{Gooian and Grayhead Intervention}

The Metalmen were a larger empire than either the Gooians or the Grayheads; however, they were not interested in Earth. The Metalmen who had came to Earth were actually commanded by a rogue general who had taken his smaller force in an attempt to claim Earth for himself. However, the Gooians and Grayheads took their entire force to Earth.

The Gooians arrived first, and planted their forces in Eastern Europe. With their superior numbers and alien weaponry, combined with their ability to use their spaceships to flush out the penguin navy, expanded into Russia and Western Europe, being stopped at the Berlin Wall by the Western forces and stopped at the boundary of Siberia by the combined bear/Metalmen forces. The Soviet military, already depleted by the years of warfare with the bears, was almost completely destroyed. The Soviet leaders were forced to flee to the nearby European nations, already under siege by a combined giraffe/penguin assault.

Meanwhile, the Grayheads planted themselves into Canada and South America. Since the South American nations had donated most of their militaries to the Americas and to Europe, they were very swiftly overwhelmed. However, the territory that the Crocdile people had captured was in this territory. The Grayheads were extraordinarily brutal, and this surprised the Crocodiles. Thus, they declared war on the Grayheads too.

At this stage in the war, chances appreared very grim for humanity. Most of the world's landmass had been occupied by foreign powers. America was fighting a two front war between the Crocodiles and the Grayheads. The remains of the forces in Western Europe were fighting the Gooians and the forces of Africa, although the Gooians were also fighting the combined Bear-Metalmen forces and the African forces were not as united as they seemed.

\subsection{A United Humanity}

Australia had remained largely untouched by both alien and animal forces. Although some of the Giraffe forces had begun water assaults, the Penguin people largely did not give them their support after some diplomatic failings and humanity was still dominant in the continent.

In desperation, the remaining human governments formed a single-government treaty and covertly moved their nuclear missiles to Australia. This was allowed by the Upper Council, as the war had quickly escalated out of their hands and they wanted a more decisive end to it. There were five original targets: the motherships belonging to the Grayheads, Gooians, and Metalmen, the Penguin capital in Antartica and the Grayhead capital in Brazil.

However, the Gooians had managed to intercept the plan. Strategically, they sent in a covert spy unit that disarmed the missile aimed towards their mothership. The rest of the missiles hit their intended targets. This essentially halted the Grayhead's expansion, as well as the Penguin's navy support and dissolved the already tenuous Bear-Metalman alliance. The Crocodiles opportunistically began taking territory in Central America back while the Grayheads recoiled.

The Single-Government President made a statement threatening to destroy the remaining capitals of the invasive forces if a peace treaty was not made involving the Grayheads and Gooians completely leaving Earth and the animal forces taking humiliating territorial concessions. This was seen as an act of intense aggression, but had the intended effect. The Grayheads began to move out of Canada, even if the Gooians had begun to take their place.

Unbeknownst to the rest of the combatants, the Grayheads were not here to conquer. Their "mothership" was actually their last remaining colony ship, after their planet had fallen to an intergalactic conqueror. With their only hope of retreating from Earth destroyed, they were now fighting for survival. Seeing this, the Upper Council approached them in order to make a deal.

\subsection{The Sinking of Australia}

The Upper Council had enacted the Couscous Protocol in the efforts of gaining control, but instead had completely lost it by 1961. Nearly every side of the war was fighting every other side; even the animal forces had turned on eachother. The humans were threatening to nuke most of the world, and the Crocodiles and Bears had found nuclear missiles as well and were making similar threats. They decided upon a plan that would frame the Grayheads.

They presented the Grayhead leadership with a seismic device, capable of leveling entire continents, developed by their R\&D teams. It could easily be presented as alien technology. Using their last flying saucer, the Grayheads would plant the device in Australia, sinking it.

The plan worked. Since every side in the war had thrown their entire military at Australia, the casualties were catastrophic. It is estimated that over three billion sapient entities died when the continent crumbled up and sank into the ocean. It was a truly sobering moment that every side in the war felt.

Now with everyone under their control, the Upper Council began work on their peace treaty.

\subsection{The Peace Treaty}

The world would be divided up by their approximate conquered territories. Canada and the United States became largely populated by Gooians, Grayheads, Crocodiles, and the remaining humans. Central and South America was divided between the Crocodiles, Penguins, and Grayheads. Africa was largely controlled by animal forces, alongside the remaining human countries who had survived the war. Western Europe was almost entirely human, while Eastern Europe became almost entirely Gooian. Asia was populated in large by Gooians, Metalmen, and animals.

Each side had a lingering resentment towards the other. Terrorist attacks in defiance of the new world order became common. However, by the 1980's, in the process of interbreeding and exchanging ideas, the races became more accustomed to eachother. Cultures were interchanged, technology was improved, and it seemed as if world peace was settling in.

Of course, this was largely due to the Upper Council enforcing their control over nearly aspect of society. But no one seemed to notice or even care.

\subsection{What Actually Matters To The Series}

The Upper Council installs Roth Darkmond to control Reno. Reno is strategically important to the Upper Council as it contains one of the highest amounts of race diversity in the world, making it a center for political power. Officially, Darkmond is the proprietor of the local power plant. Unofficially, Darkmond is slowly expanding his control over the entirety of Reno.

Klamath Tellth, the son of two Gooian immigrants and amateur private eye, begins to suspect that there is a conspiracy when a mathematical error occurs in his electrical bill. He originally suspects that the Zirconium Corporation, run largely by Metalmen, is responsible for the conspiracy. During his investigation and resulting gunfire incidents, he largely wipes out the Zirconium Corporation's leadership, allowing Darkmond to expand his control even furhter.

Klamath, now enraged, decides to try to expose Darkmond's evil schemes, but appears insane and humiliates himself, losing most of his private eye business. With help from his brother, he managed to find work as a fluff journalist. However, he accidentally witnesses Darkmond executing a rival businessman and deciedes to resume his investigations.

\section{Style}

Detective Klamath should have a style, even if said style is "scuffed".

\subsection{Visual}

Characters should be visually very simple and reducible to a few common shapes. Try to avoid creating visual noise. This is accomplished by contrasting the characters against their backgrounds. The colors and style of a character should be different from that of the background.

Movements should be as fluid as possible. Animate on twos to provide the nostalgic 70's animation look and feel. Also use armatures and tweening as often as possible. It may not look as good as hand-animation, but the visuals should take a backseat to a compelling/funny plot.

\subsection{Musical}

Music should use the symbols and the saxophone as motifs, in order to create a candied version of the 1920's noir asthetic. I'm not a music guy, but I feel like sticking to a solid motif will make the show more memorable.

\subsection{Writing}

A random list of tips for what I want each episode to feel like, writing-wise.

Each episode should feature a balance of comedy and drama. However, the writing should never take itself too seriously. Comedies are always better when their plots have a little tongue in their cheek. It's better to be cheesy than edgy.

Dry wit and irony should be the pioneering style of the humor. Wordplay comes second. NEVER use reference humor or gross-out humor. We're not Family Guy. Self referential humor is fine, but keep it to 1-2 jokes per episode.

\textbf{No rape jokes. No rape references. Any possible humor or drama that can be extracted from rape is not worth the edge and weight it introduces into the episode. In fact, if I grep the script and see the word "rape", I'll just delete it, since whatever circumstances lead to a rape reference in the script probably mean the script as a whole has significant problems.}

Motive should always be clear and established at every point. Especially for visual storytelling, keeping a decent voltage throughout the story is important. The reason why Klamath is going on whatever adventure is going on should be established early on, and at any given point, the question "why is Klamath still here?" should be able to be answered very easily.

Cursing should be kept to a minimum. It is better to be cheesy than to be edgy. Cheesy things are mocked at first but become irreverant. Edgy things seems like they'll become irreverant but eventually become mocked.

Instead of cursing, don't do shocked silence instead. Clever writing can fill that hole.

Aside from that, just keep your wits about you. Write before you write; outline like the world depends on it; make sure to pass around the script to people who know what they're doing.

\section{Characters}

Each character in Detective Klamath should serve an important role in the series, providing either levity, comedy, drama, or plot advancement. They are described below, along with how they should be used.

\subsection{Klamath}

Klamath Tellth was born to a pair of immigrants who came from the Gooian homeworld of Sigma 9. Growing up, he was always in the shadow of his brother, Donald. However, he did always look up to Donald. When Donald became a private investigator, Klamath followed suite. However, when Donald started to break big cases and acquire world reknown for it, Klamath started to look for his own case.

Klamath stumbled onto the Darkmond conspiracy by accident, after a mathematical error in one of his electric bills. Originally, Klamath blamed the Zirconium Corporation; a military industry manufacturer based in Reno. Through resorting to methods that other private investigators wouldn't (dumpster diving, impersonating officials), Klamath discovered evidence that the Zirconium Corporation was developing a world-ending weapon.

However, he was arrested by the Zirconium-controlled police department and put on death row. Against all odds, Klamath fought his way out of prison and into the Zirconium headquarters, where he destroyed the Hummingbird Engine and dissolved Zirconium. However, this only allowed Darkmond to gain more control over Reno.

Realizing his folly, Klamath began trying to expose Darkmond. However, Darkmond covered his tracks and preventing Klamath from acquiring any leads. This eventually drove Klamath to insanity, and ended in his going nude off of Main Street and ranting about Darkmond's supposed crimes. Donald paid his bail for public nudity and, as his private eye business had dried up, gave him a job as a reporter for the Daily Stew.

Life as a reporter bored Klamath, however, and, after witnessing Darkmond assassinate a political rival right ouside of his office building, he quit his job to resume being a private eye. Over the course of the first season, Klamath finds evidence of the conspiracy that inevitably spirals into involvement with another body of power that inevitably destroys the evidence.

Klamath is, first and foremost, an optimist. Even he realizes how rediculous his Quioxote-esque quest is, but he continues on regardless. However, this makes him restless. He often pursues the quickest action available to him, regardless of whether or not it's effective. In addition, he has a single-minded vision of what he has to accomplish. He tends to see the endpoints, rather than the parts in-between. He is reluctant to change those endpoints.

Secondly, Klamath is an eccentric. He sees a different way of seeing and doing things that, while understandable, may be strange. Thirdly, Klamath is driven to the point of exhaustion. Fourth, Klamath tends to idolize pop culture trends; hence, how he presents himself as a detective.

Due to his eccentricities and general circumstances of bad luck, Klamath botches all of the evidence that he collects. As Klamath investigates Darkmond, his brother Donald catches wind of it while trying to disprove the conspiracy and investigates it. His more successful investigations lead to him presenting his evidence in front of the city's council. However, the city's council is controlled by Darkmond, who then proceeds to murder Donald by throwing him off of the city's dam.

In invisible ink on a slip of paper held by Donald, Klamath finds a clue leading to Donald's black book of clues, which all extend Klamath's former pieces of evidence. He uses this to persuade Mr. Observant, an anti-trust agent Klamath had accidentally spurned, to look into Darkmond again. Klamath, with vengeance in his heart, decides to expose Darkmond on local news. However, Darkmond controls the local news. In a shootout, Klamath kills Darkmond.

The incident becomes national news and leads to Klamath's rise in fame. However, increased stress from new investigations, a lack of purpose from having finally accomplished his life's goal, and the loss of his brother lead to Klamath becoming addicted to amphetamines. Shirley tries to help him kick his addiction, but he eventually relapses. During this bender, he witnesses Shirley killed by the Upper Council, which he has been finding clues in regards to Darkmond. He also gets shot by the gunman (who is actually Clearway), causing him to lose his left eye and part of his brain.

His investigations into the Upper Council lead him into a trap, where Upper Council "messengers" take his right arm and tell him there is a bomb hidden under his house capable of blowing up all of Reno. Seeing that he has the choice of either running away and living with the guilt, or trying to stop the bomb, he drives back to Reno and finds that the bomb is under his house, guarded by Doc Chester. A shootout with Doc Chester leaves Klamath fatally wounded; with his dying breath, he disarms the bomb.

Ironically, due to the circumstances of his death, the public at large believes it was Klamath that built the bomb and Doc Chester who disarmed it.

\subsection{Doc Chester}

Jack "Doc" Chester (no PhD) is a scientist and inventor. Born to human parents, he quickly blew his peers away with his intelligence and laziness. Despite his gifts, he barely graduated high school, disappointing his parents.

He started taking up odd jobs, but these jobs inevitably lead to his clients getting killed or worse. This leads to him becoming more emotionally jaded, and appearing to be insane as a cover. Although he is capable of great feats, his short attention span and overall laziness mean his inventions are a novelty at best.

He answered an ad for a forensic scientist that Klamath put out at one point, despite not having any training in forensics. This led to Klamath and Chester becoming fast friends, and eventually roommates after Klamath's former roommate gets fed up with his eccentricities. Chester often accompanies Klamath on his investigations, providing input and acting as his confidante.

Eventually, Chester has a midlife crisis around the same time Klamath is jailed for public nudity. For the first time in his life, he applies for a real job at the Applied Containment Institution; however, due to Chester's laziness, he never realizes that he's working for a paranormal investigation lab instead of just a regular lab.

However, this puts him in contact with the Upper Council. Chester follows Klamath along his adventures, largely just because he has nothing else to do. Often, this leads him Eventually, the Upper Council contacts him and tells him to build a bomb underneath Reno. He does this; however, Klamath finds him and they enter a shootout. Klamath kills Chester; however, in his last breath, Chester fatally wounds Klamath.

Due to the fact that he used Klamath's credit cards and basement to build the bomb, the public at large believes Klamath built the bomb and Chester defused it.

\subsection{Shirley Signage}

Shirley Signage was the product of an experiment to create the perfect police officer. Sensodryme was injected into various government parapharilia, making them sapient. The product was eventually abandoned, leaving all of the resulting entities free to do what they will. Having no parental figures or real childhood, Shirley turned to Catholicism to fill the void. In trying to find her greater purpose, Shirley moved to Reno, became a police officer and married a Grayhead businessman.

However, she soon hit "the Wall". She was demoted to be a simple beat cop, lost all love for her husband, and even started losing her faith. It's at this point that Klamath found Shirley, as she was the first police officer he talked to during the Darkmond investigation, and mistakenly gave him her number. This made her the subject of Klamath's idolization for the next few years, as he saw her as his "police contact".

Shirley witnessed Klamath's downfall and then begin to rise. At first, she only interacted with him out of coincidence, or Klamath calling 911. However, she eventually started going on Klamath's adventures willingly. She told herself that she was looking for reasons to arrest Klamath; however, with her divorce ongoing and her faith severed, she followed Klamath because he was one of the few things she really believed in. There was also some romance that Klamath was not interested in.

Shirley helped Klamath in the shootout against Darkmond. Shirley often accompanied Klamath, hiring him as a private contractor for certain cases. However, she was the first to notice Klamath's descent into amphetamine addiction. Trying to prevent him from falling into the same hole she fell into, she tried her best to rehabilitate him. However, she failed, sending him on a bender. At this point, the Upper Council, deciding that Shirley was getting to involved in their plans, and assassinated her, presenting it as a gang shooting.

\subsection{Roth Darkmond}

Roth Darkmond was born to two Upper Councilmen. He was inserted into their secret hierarchy at an early age. He was selected to control Reno, which the Upper Council predicted would become an important city due to its high levels of diversity. Propoganda asserts that Darkmond is a self-made industrialist who has an investment in the city's future; in reality, his goal is to control as much of Reno as he can, so that the Upper Council can control it when the time is right.

However, due to Darkmond's priveleged upbringing, he really has no idea how to run this criminal conspiracy. After he discovers Klamath has discovered his conspiracy, he devotes nearly all of his time to stifling Klamath's investigations, often ineffectively. However, he manages to destroy whatever evidence Klamath has on him by the end of the episode, enforcing the status quo.

During this time, Donald also starts investigating Darkmond. While Donald is presenting evidence of the Darkmond conspiracy, Darkmond reveals that the mayor and his staff are actually robots that he controls, and then knocks out Darkmond with nitrous oxide. In order to stage his suicide, Darkmond throws Donald off of the Truckee Dam.

\section{Episodes}

Detective Klamath should have 2 seasons, with about 10 episodes per season. The first 5 episodes establish a pattern, and the next 5 break it.

\end{document}